% Austin Hardaway's Resume


\documentclass[margin,line]{resume}

\usepackage{graphicx}

\begin{document}

\name{\huge \sc{Austin Hardaway}\vspace{2mm}}
{
    \hfill austinhardaway@gmail.com       \vspace{0mm}\\\vspace{0mm}%
    \hfill http://austinhardaway.github.io         \vspace{0mm}\\\vspace{0mm}%
    \hfill https://github.com/austinhardaway \vspace{0mm}\\\vspace{0mm}%
    \hfill https://www.linkedin.com/in/austinhardaway/ \vspace{0mm}\\\vspace{0mm}%
    \hfill 903-343-1017 \vspace{0mm}\\\vspace{-9mm}%

}

\begin{resume}

    \vspace{-3mm}

    %__________________________________________________________________________________________________________________
    % Summary
    \section{\mysidestyle \textbf{\large{S}\small{UMMARY}}}

    Senior at UGA pursuing a double major in Computer Science and Mathematics with an area
    of emphasis in Applied Mathematics. I have a passion for creating and making through software and am interested in opportunities to help me cultivate that passion.

    \vspace{-1mm}

\sectionline

    %__________________________________________________________________________________________________________________
	% Education
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \textbf{\listing University of Georgia}, Athens, Georgia \vspace{1mm}\\
    \textsl{Computer Science and Mathematics - GPA:3.1} \hfill \textbf{August 2015 -- May 2019}\vspace{-3mm}\\\vspace{-1mm}%
	\\Dean's List Fall 2015, Spring 2018
	\\Active UGA Mock Trial Competitor 2015-2018 

    \vspace{-1mm}

	\sectionline

    %__________________________________________________________________________________________________________________    
    % Professional Experience
    \section{\mysidestyle \textbf{\large{P}\small{ROFESSIONAL} \large{E}\small{XPERIENCE}}}

	% Macy's @TODO: Update with more clear responsibilites
    \textbf{\listing Macy's Technology} \vspace{2mm}\\\vspace{1mm}%
    \textsl{DevOps Intern} \hfill \textbf{May 2018 -- August 2018}\\
    10 week internship with the DevOps team in Johns Creek at Macy's Technology.

    % WoodmenLife
    \textbf{\listing WoodmenLife} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineering Intern} \hfill \textbf{May 2016 -- July 2016}\\
    Summer internship, I was placed on an agile based team of developers and
had a comparable workload as a full-time junior developer.
Throughout the course of the program I completed tickets that ranged the entire
Java/Spring stack. (Java/Spring/MySQL/JSP)
As a capstone i was responsible for designing and implementing a new messaging feature from the ground up
designing the views, creating the tables, etc.
\\\\
    % iFixit
    \textbf{\listing UGA Office of STEM Education} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Peer Learning Assistant/TA} \hfill \textbf{June 2012 -- August 2014}\\
    I TA CSCI 1301, a rigorous introduction to programming. It's a large lecture format and taught in Java, I am responsible for
grading assignment submissions and helping students troubleshoot their lab assignments.
During this past year I have helped create 2 new lab assignments, this includes having an idea which exhibits specific skills (2D arrays, string manipulation, etc) and then creating any external classes the students may need as well as creating grading and instruction documents.\\ 
Additionally I have written and shared numerous grading scripts which automate the process of grading sometimes upward of 100-150 command line applications. These scripts are usually written in the bash scripting language and sometimes require Java Reflection and/or JUnit testing.


\sectionline

    %__________________________________________________________________________________________________________________
   
    % Skills / Keywords
    \section{\mysidestyle \textbf{\large{S}\small{KILLS} }}

    \textbf{Linux:} Red Hat family, Debian family (Ubuntu, Debian)\\
    \textbf{Scripting:} Bash, Python, Ruby\\
    \textbf{Backend:} Python, Java (Spring), C/C++\\
    \textbf{Frontend:} HTML, CSS and Less, Javascript (jQuery)\\
    \textbf{Databases:} MySQL, firebase, H2\\
    \textbf{Version control systems:} Git, Subversion\\
    
\end{resume}
\end{document}
